A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-12-29 pilot-publication/lab-book.Rmd
Edit code to generate outcome tables

```{r setup}
library(pbapply)
library(openssl)
library(dotenv)
library(DataExplorer)
```

@@

## Create outcome tables
create_ci_level_tables <- function(table.name, ci.data) {
    print(table.name)
    table.data <- ci.data[grep(table.name, names(ci.data), fixed = TRUE)]
    column.names <- strsplit(names(table.data), split = "\\|\\|\\.") %>%
        lapply(function(column) column[2]) %>%
        unique() %>%
        stringr::str_replace_all(pattern = "\\|\\|column\\:\\:", replacement = "")
    row.names <- strsplit(names(table.data), split = "\\|\\|\\.") %>%
        lapply(function(row) row[3]) %>%
        unique() %>%
        stringr::str_replace_all(pattern = "\\|\\|row\\:\\:index\\:[0-9]*\\:\\:", replacement = "") %>%
        stringr::str_replace_all(pattern = "\\|\\|", replacement = "")
    ci.table <- matrix(table.data, ncol = length(column.names)) %>%
        tibble::as_tibble(.name_repair = "minimal") %>%
        tibble::add_column(row.names, .before = 1, .name_repair = "minimal") %>%
        setNames(c("Outcome", column.names))
    return(ci.table)
}

tables <- lapply(
    combined.outcome.results, function(ci.data) {
        lapply(table.names, create_ci_level_tables, ci.data = ci.data)
    }
)

outcome.results.data <- enframe(outcome.results$point.estimates)
table.names <- strsplit(names(outcome.results$point.estimates), split = "\\|\\|\\.")
```

>>>>

```{r setup}
library(pbapply)
library(openssl)
library(dotenv)
library(DataExplorer)
noacsr::source_all_functions()
```

@@

## Create outcome tables
create_ci_level_tables <- function(table.name, ci.data) {
    print(table.name)
    table.data <- ci.data[grep(table.name, names(ci.data), fixed = TRUE)]
    column.names <- strsplit(names(table.data), split = "\\|\\|\\.") %>%
        lapply(function(column) column[2]) %>%
        unique() %>%
        stringr::str_replace_all(pattern = "\\|\\|column\\:\\:", replacement = "")
    row.names <- strsplit(names(table.data), split = "\\|\\|\\.") %>%
        lapply(function(row) row[3]) %>%
        unique() %>%
        stringr::str_replace_all(pattern = "\\|\\|row\\:\\:index\\:[0-9]*\\:\\:", replacement = "") %>%
        stringr::str_replace_all(pattern = "\\|\\|", replacement = "")
    ## Replace outcome names with labels
    all.outcomes <- all_outcomes()
    outcomes.column <- sapply(row.names, function(row.name) {
        if (!is.null(all.outcomes[[row.name]])) {
            return(all.outcomes[[row.name]]$label)
        } else {
            return(row.name)
        }
    })
    ## Create table
    ci.table <- matrix(table.data, ncol = length(column.names)) %>%
        tibble::as_tibble(.name_repair = "minimal") %>%
        tibble::add_column(outcomes.column, .before = 1, .name_repair = "minimal") %>%
        setNames(c("Outcome", column.names))
    return(ci.table)
}

tables <- lapply(
    combined.outcome.results, function(ci.data) {
        {
            lapply(table.names, create_ci_level_tables, ci.data = ci.data)
        } %>%
            setNames(stringr::str_replace(table.names, pattern = "\\|\\|table\\:\\:", replacement = ""))
    }
)
```
